CommonMind Consortium: DLPFC

### 2020-09-17 combined_analysis/diff.networks.Rmd
Update diff networks

```{r modules.in.discovery, fig.width=10, fig.height=20}

@@

@@

```{r modules.in.second.cohort, fig.width=8, fig.height=100}

@@

```{r modules.in.discovery.Dx, fig.width=10, fig.height=20}

@@

X = matrnorm(300, 1000)

@@

C = C_x[1:5, 1:5]
colnames(C) = paste0('gene_', 1:5)
rownames(C) = colnames(C)

>>>>

```{r modules.in.discovery, fig.width=10, fig.height=50}

@@

	plot_module( mod, df_test, METADATA, dynamicColors, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt", 5)   
	})

@@

```{r modules.in.second.cohort, fig.width=8, fig.height=25}

@@

```{r modules.in.discovery.Dx, fig.width=10, fig.height=50}

@@

X = matrnorm(1000, 30)

@@

C = C_x[1:5, 1:5]
colnames(C) = paste0('gene_', 1:nrow(C))
rownames(C) = colnames(C)
